MSA Asthma Place of Service Timeseries

### 2018-06-11 r_scripts/analysis/asthma_place_of_service_analysis.Rmd
updated some stuff.

```{r other_msa}
other_msa_result <- asthma_pos_list[c(1,3:5,7)] %>% 
  map_dfr(., function(df){
    service_place <- as.character(df$service_place[1])
    # complete case
    df <- df %>% filter(!is.na(geo_smk10)) %>% 
      filter(metroarea != "Medford") %>% 
      filter(metroarea != "Not in MSA")
    # model
    mod <- clogit(outcome ~ geo_smk10 + wrf_temp + strata(identifier), 
                  data = df)
    # n events
    n_events <- mod$nevent
    # odds ratio and 95% CI
    estimates <- broom::tidy(mod) %>% 
      filter(term == "geo_smk10") %>% 
      dplyr::select(term, estimate, conf.low, conf.high) %>% 
      mutate_at(2:4, funs(round(exp(.),3))) %>% 
      cbind(service_place, n_events, .) %>% 
      mutate(service_place = as.character(service_place))
  }) %>% 
  mutate(strata = "Total") %>% 
  dplyr::select(strata, service_place:conf.high) %>% 
  rename(odds_ratio = estimate, lower95 = conf.low, upper95 = conf.high) %>% 
  mutate(MSA = "Other",
         service_place = case_when(service_place=="Ambulance-Land"~"Ambulance",
          service_place == "Emergency Room – Hospital" ~ "Emergency Room",
          TRUE ~ service_place),
    # set order of service place
          service_place = factor(service_place, 
            levels = c("SABA Fill", "Office", "Outpatient Hospital", 
                       "Emergency Room", "Inpatient Hospital")))

# table
other_msa_result
```

@@

```{r medford_plot}
msa_results <- bind_rows(medford_result, other_msa_result)
# plot total results
med_plot <- ggplot(msa_results, aes(x = service_place, y = odds_ratio)) +
  geom_point(color = "purple") + 
  geom_errorbar(aes(ymin=lower95, ymax=upper95), color = "purple",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~MSA) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Place of Service") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust =1),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

>>>>

```{r other_msa}
msa <- unique(asthma_pos_list[[1]]$metroarea)

msa_result <- asthma_pos_list[c(1,3:5,7)] %>% 
  map_dfr(., function(df){

    service_place <- as.character(df$service_place[1])
    # complete case
    pos_list <- df %>% filter(!is.na(geo_smk10)) %>% 
      filter(metroarea != "Not in MSA") %>% 
      split(.$metroarea) %>% 
      map_dfr(., function(df2){
        # find msa
        msa <- as.character(df2$metroarea[[1]])
        # runm odel
        mod <- clogit(outcome ~ geo_smk10 + wrf_temp + strata(identifier), 
                      data = df2)
      # n events
      n_events <- mod$nevent
      # odds ratio and 95% CI
      estimates <- broom::tidy(mod) %>% 
        filter(term == "geo_smk10") %>% 
        dplyr::select(term, estimate, conf.low, conf.high) %>% 
        mutate_at(2:4, funs(round(exp(.),3))) %>% 
        cbind(service_place, msa, n_events, .) %>% 
        mutate(service_place = as.character(service_place),
               msa = as.character(msa))})
  }) %>% 
  mutate(strata = "Total") %>% 
  dplyr::select(strata, service_place:conf.high) %>% 
  rename(odds_ratio = estimate, lower95 = conf.low, upper95 = conf.high) %>% 
  mutate(MSA = "Other",
         service_place = case_when(service_place=="Ambulance-Land"~"Ambulance",
          service_place == "Emergency Room – Hospital" ~ "Emergency Room",
          TRUE ~ service_place),
    # set order of service place
          service_place = factor(service_place, 
            levels = c("SABA Fill", "Office", "Outpatient Hospital", 
                       "Emergency Room", "Inpatient Hospital")))

# table
msa_result
```

@@

```{r medford_plot}

# plot total results
med_plot <- ggplot(msa_result, aes(x = service_place, y = odds_ratio)) +
  geom_point(color = "purple") + 
  geom_errorbar(aes(ymin=lower95, ymax=upper95), color = "purple",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~msa, scales = 'free_y') +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Place of Service") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust =1),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

### 2018-06-11 r_scripts/analysis/msa_asthma_timeseries.Rmd
updated some stuff.

```{r pos_plot}
pos_plot = ggplot(asthma_weekly_count, 
  aes(x=week_date, y=rate_100k, group = service_place, color=service_place)) +
  geom_point(size = 1.25) +
  scale_color_manual('Care Utilization', 
    values = c("#3c1053", "#7f00ff", "#e100ff", "#00b09b", "#0ed2f7", "#c31432")) +
  facet_wrap(~metroarea, ncol=1) +
    ylab("Weekly Rate per 100,000 Persons") +
    xlab("Date") +
    ggtitle('B. Asthma Care Utilization') +
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_text(angle = 90),
        legend.key = element_blank())

@@

# read zip pm; join with msa
msa_pm = read_csv('./data//pm/2013-oregon_zip_pm25.csv', 
                  col_types = cols(ZIPCODE = 'c')) %>% 
    # join with unique MSA vector
    left_join(zip_msa, by = 'ZIPCODE') %>%
    # mutate
    mutate(ZIPCODE = as.factor(ZIPCODE),
        MSA = as.factor(MSA),
        # assign metro name to number
        metroarea = case_when(MSA == 13460 ~ "Bend",
                              MSA == 18700 ~ "Corvallis",
                              MSA == 21660 ~ "Eugene",
                              MSA == 32780 ~ "Medford",
                              MSA == 38900 ~ "Portland",
                              MSA == 41420 ~ "Salem"))  %>% 
    # filter to zips in an MSA only
    filter(!is.na(metroarea)) 
```

@@

```{r pm_plot}
# plot of pm by msa
pm_msa_plot = ggplot(data = msa_pm, aes(x = date, y = geo_smk_pm, group = ZIPCODE)) +
    geom_line(color = '#e94057') +
    # facet by metro area
    facet_wrap(~metroarea, ncol = 1) +
    # y label
    ylab(expression(paste("Wildfire Smoke PM"[2.5]," 10µg/m"^3))) +
    # x label
    xlab("Date") +
    ggtitle(expression(paste('A. Wildfire Smoke PM'[2.5]))) +
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_text(angle = 90))

@@

@@

```{r save_df, eval=F}
# write asthma weekly count
#write_csv(asthma_weekly_count, './data/health/asthma_weekly_count.csv')
# write pm msa
#write_csv(msa_pm, './data/pm/msa_pm.csv')
```

@@

>>>>

```{r pos_plot}
pos_plot <- ggplot(asthma_weekly_count, 
  aes(x=week_date, y=rate_100k, group = service_place, color=service_place)) +
  geom_point(size = 1.25) +
  scale_color_manual('Care Utilization', 
    values = c("#3c1053", "#7f00ff", "#e100ff", "#00b09b", "#0ed2f7", "#c31432")) +
  facet_wrap(~metroarea, ncol=1) +
    ylab("Weekly Rate per 100,000 Persons") +
    xlab("Date") +
    ggtitle('B. Asthma Care Utilization') +
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_text(angle = 90),
        legend.key = element_blank())

@@

# read zip pm; join with msa
msa_pm <- read_csv('./data//pm/2013-oregon_zip_pm25.csv', 
                  col_types = cols(ZIPCODE = 'c')) %>% 
    # join with unique MSA vector
    left_join(zip_msa, by = 'ZIPCODE') %>%
    # mutate
    mutate(ZIPCODE = as.factor(ZIPCODE),
        MSA = as.factor(MSA),
        # assign metro name to number
        metroarea = case_when(MSA == 13460 ~ "Bend",
                              MSA == 18700 ~ "Corvallis",
                              MSA == 21660 ~ "Eugene",
                              MSA == 32780 ~ "Medford",
                              MSA == 38900 ~ "Portland",
                              MSA == 41420 ~ "Salem"))  %>% 
    # filter to zips in an MSA only
    filter(!is.na(metroarea)) 
```

@@

```{r pm_plot}
# plot of pm by msa
pm_msa_plot <- ggplot(data = msa_pm, aes(x = date, y = geo_smk_pm, group = ZIPCODE)) +
    geom_line(color = '#e94057') +
    # facet by metro area
    facet_wrap(~metroarea, ncol = 1) +
    # y label
    ylab(expression(paste("Wildfire Smoke PM"[2.5]," 10µg/m"^3))) +
    # x label
    xlab("Date") +
    ggtitle(expression(paste('A. Wildfire Smoke PM'[2.5]))) +
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_text(angle = 90))

@@

### Monthly Rate and Sum by MSA

```{r monthly_counts_msa}
monthly_msa_counts <- asthma_pos_count %>% 
  mutate(month = lubridate::month(date)) %>% 
  group_by(month, metroarea, service_place) %>% 
  summarise(n_events = sum(n_events)) %>% 
  left_join(population, by = 'metroarea') %>% 
  mutate(rate_100k = (n_events/pop)*100000,
         month_name = factor(case_when(month == 5 ~ 'May',
                                       month == 6 ~ 'Jun',
                                       month == 7 ~ 'Jul',
                                       month == 8 ~ 'Aug', 
                                       month == 9 ~ 'Sep'),
                        levels = c('May', 'Jun', 'Jul', 'Aug', 'Sep'))) %>% 
  filter(service_place != 'Ambulance-Land') %>% 
  filter(service_place != 'Urgent Care Facility') %>% 
  filter(!is.na(pop)) %>% 
  arrange(service_place, metroarea, month)
```

Plot montly rate by MSA.

ED Rate

```{r ed_plot}
ed_count <- monthly_msa_counts %>% filter(service_place == 'Emergency Department')

# plot
ed_plot <- ggplot(ed_count, aes(x = month_name, group = metroarea,
                                        fill = metroarea)) +
  geom_bar(aes(weight = rate_100k)) +
  scale_fill_manual("Metro Area", values = c("#3c1053", "#7f00ff", "#e100ff", 
                                             "#4389a2", "#0ed2f7", "#74ebd5"),
                    guide = F) +
  facet_wrap(~metroarea, ncol =1) +
  ylab("Monthly Rate per 100,000 Persons") +
  xlab("Date") +
  ggtitle('A. ED') +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_text(angle = 90),
        legend.key = element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1))

ed_plot
```

Outpatient.

```{r outpat}
out_count <- monthly_msa_counts %>% 
  filter(service_place == 'Outpatient Hospital')
# plot
out_plot <- ggplot(out_count, aes(x = month_name, group = metroarea,
                                        fill = metroarea)) +
  geom_bar(aes(weight = rate_100k)) +
  scale_fill_manual("Metro Area", values = c("#3c1053", "#7f00ff", "#e100ff", 
                                             "#4389a2", "#0ed2f7", "#74ebd5"),
                    guide = F) +
  facet_wrap(~metroarea, ncol =1) +
  xlab("Date") +
  ggtitle('B. Outpatient') +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1))

out_plot
```

Inpatient.

```{r outpat}
inpat_count <- monthly_msa_counts %>% 
  filter(service_place == 'Inpatient Hospital')
# plot
inpat_plot <- ggplot(inpat_count, aes(x = month_name, group = metroarea,
                                        fill = metroarea)) +
  geom_bar(aes(weight = rate_100k)) +
  scale_fill_manual("Metro Area", values = c("#3c1053", "#7f00ff", "#e100ff", 
                                             "#4389a2", "#0ed2f7", "#74ebd5"),
                    guide = F) +
  facet_wrap(~metroarea, ncol =1) +
  ylab("Monthly Rate per 100,000 Persons") +
  xlab("Date") +
  ggtitle('C. Inpatient') +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1))

inpat_plot
```

Office.

```{r office}
off_count <- monthly_msa_counts %>% 
  filter(service_place == 'Office')
# plot
off_plot <- ggplot(off_count, aes(x = month_name, group = metroarea,
                                        fill = metroarea)) +
  geom_bar(aes(weight = rate_100k)) +
  scale_fill_manual("Metro Area", values = c("#3c1053", "#7f00ff", "#e100ff", 
                                             "#4389a2", "#0ed2f7", "#74ebd5"),
                    guide = F) +
  facet_wrap(~metroarea, ncol =1) +
  ylab("Monthly Rate per 100,000 Persons") +
  xlab("Date") +
  ggtitle('D. Office') +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1))

off_plot
```

SABA fill.

```{r saba}
saba_count <- monthly_msa_counts %>% 
  filter(service_place == 'SABA Fill')
# plot
saba_plot <- ggplot(saba_count, aes(x = month_name, group = metroarea,
                                        fill = metroarea)) +
  geom_bar(aes(weight = rate_100k)) +
  scale_fill_manual("Metro Area", values = c("#3c1053", "#7f00ff", "#e100ff", 
                                             "#4389a2", "#0ed2f7", "#74ebd5")) +
  facet_wrap(~metroarea, ncol =1) +
  ylab("Monthly Rate per 100,000 Persons") +
  xlab("Date") +
  ggtitle('E. SABA') +
  theme_minimal() +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted',
                                        size = 0.5),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1))

saba_plot
```

Join all plots.

```{r msa_rate_plot}
# save plot
#tiff('./r_scripts/analysis/Figs/msa_month_rate.tiff', width = 800, height = 600)
gridExtra::grid.arrange(ed_plot, out_plot, inpat_plot, off_plot, saba_plot, 
                        ncol=5, widths = c(0.2, 0.2, 0.2, 0.2, 0.3))
#dev.off()
```

Compare August to July and September for each MSA.

Model
```{r rate_compare}
metro <- unique(monthly_msa_counts$metroarea)
service_place <- unique(monthly_msa_counts$service_place)
month <- seq(5,9,by=1)
# expand grid
month_msa <- expand.grid(metro, service_place, month) %>% 
  rename(metroarea = Var1, service_place = Var2, month = Var3)

summary(outcome_list)
# create outcome list
outcome_list <- month_msa %>% 
  left_join(monthly_msa_counts, by = c("metroarea", "service_place", "month")) %>% 
  mutate(n_events = ifelse(is.na(n_events), 0, n_events),
         pop = ifelse(is.na(pop), 85934, pop),
         month_name = factor(case_when(month == 5 ~ 'May',
            month == 6 ~ 'Jun',
            month == 7 ~ 'Jul',
            month == 8 ~ 'Aug', 
            month == 9 ~ 'Sep'),
            levels = c('May', 'Jun', 'Jul', 'Aug', 'Sep'))) %>% 
  split(.$service_place)

# function list
compare_df <- outcome_list %>% 
  map_dfr(., function(df){
    df <- outcome_list[[5]]
    serv_pl <- unique(df$service_place)
    serv_pl
    # model
    mod <- glm(n_events ~ 0 + metroarea*month_name + offset(log(pop)), 
                family = poisson, data = df)

    summary(mod)
    contr_msa_jul_to_sep <- rbind(
      #'Bend: Aug to Jul' = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Bend: Aug to Sept' = c(0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0),
      #'Eug: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0),
      #'Eug: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0),
      'Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Med: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0),
      'Port vs Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-.5,-.5,0,0,0,.5,.5,0,0,0,0,0,0)
      #'Port: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0),
      #'Sal: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0),
      #'Sal: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1)
      )

    # multicomp comparison of contrasts
    jul_sep_contrast <- multcomp::glht(mod, contr_msa_jul_to_sep)
    # summary of adjusted
    compare_df <- data.frame(broom::tidy(
      summary(jul_sep_contrast, test = multcomp::adjusted('none')))) %>% 
      mutate(service_place = serv_pl) %>% 
      select(service_place, lhs:p.value)
  })
compare_df
```

Test change by MSA.

```{r}
print(saba_count)
```

Fitting a time-series model to predict the observed across MSAs. I need the spline package.

```{r spline}
library(splines)
```

I want to map across each outcome and metroarea to fit splines I think. I'll first try an interaction spline by MSA for saba fills.

```{r weekly_pm}
weekly_pm = msa_pm %>% 
  mutate(week_date = lubridate::ceiling_date(date, unit = 'week')) %>% 
  group_by(metroarea, week_date) %>% 
  summarise(mu_gwr_smk = mean(geo_smk_pm), mu_gwr = mean(geo_wt_pm))

summary(weekly_pm)
```

```{r}
glimpse(asthma_weekly_count)

# vector of outcomes
out_vec = unique(asthma_weekly_count$service_place)

# list of metroareas
msa_list = asthma_weekly_count %>% 
  split(., list(.$metroarea,.$service_place))

# map to get estiamtes of counts for each 
exp_n = msa_list %>% 
  map_dfr(., function(data){
    service_place = as.character(data$service_place[1])
    metroarea = as.character(data$metroarea[1])
    # vector of dates
    week_date = as.character(data$week_date)
    # spline with 4 degrees of freedom fits msas pretty well
    spl = ns(data$week_date, df = 4)
    # fit spline to counts
    mod = glm(n_events ~  spl, family = 'poisson'(link='identity'), 
          data = data)
    # estimated outcomes
    est = predict(mod, newdata=data, type = 'response') 
    # dataframe of estimates by msa and place of service
    est_df = data.frame(cbind(service_place, metroarea, week_date, est)) %>% 
      mutate(week_date = as.Date(week_date, format = "%Y-%m-%d"),
             est = as.numeric(as.character(est)),
             metroarea = as.character(metroarea),
             service_place = as.character(service_place)) 
  }) %>% 
  left_join(asthma_weekly_count, ., 
            by = c('metroarea', 'service_place', 'week_date')) %>% 
  mutate(diff = est - n_events,
         est_rate = (est/pop)*100000,
         diff_rate = rate_100k - est_rate)

# plot of expected over observed
ggplot(data=exp_n, aes(x=week_date, y=diff_rate, 
    group = service_place, color = service_place)) +
  geom_point() +                 
  facet_wrap(~metroarea)
```

@@

```{r save_df, eval=F}
# write asthma weekly count
#write_csv(asthma_weekly_count, './data/health/asthma_weekly_count.csv')
# write pm msa
#write_csv(msa_pm, './data/pm/msa_pm.csv')
#write_csv(monthly_msa_counts, './data/monthly_counts.csv')
```

@@

```{r}
exp(-0.295)
```
